Single-step Hybrid Predition

### 2016-11-22 reports/agronomic_data.Rmd
Add legends to prediction legends

# Agronomic Data
```{r echo = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")

>>>>

# Agronomic Data
```{r setup-agro, echo = FALSE, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")

### 2016-11-22 reports/data_overview.Rmd
Add legends to prediction legends

# Data Overview
```{r message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")

>>>>

# Data Overview
```{r setup-overview, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")

### 2016-11-22 reports/impute_single_mrna.Rmd
Add legends to prediction legends

# Genotype-Wise mRNA-Imputation
```{r echo = FALSE}
pacman::p_load("sspredr", "tidyverse", "caret", "e1071", "viridis",
               "forcats", "knitr", "rmarkdown", "purrr", "rprojroot",
               "methods", "parallel")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ".", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, 
                      warning = FALSE, message = FALSE, echo = FALSE)
```

@@

```{r Plot-Correlation-Imputed-vs-NonImputed, cache = TRUE, fig.width = 12, fig.height = 12, fig.cap = "Pearson correlation coefficients between original and imputed mRNA genotypes for two heterotic groups and two sources of information (i.e. genomic and pedigree)."}
par_lst <- readRDS("./data/derived/impute_single_mrna.RDS")
par_lst %>%
  map(~keep(., is_list)) %>%
  at_depth(.depth = 2, ~bind_rows(., .id = "Group")) %>%
  map(~bind_rows(., .id = "Replication")) %>%
  bind_rows(.id = "Data_Type") %>%
  mutate(Data_Type = fct_recode(Data_Type,
                                Genomic = "snp_lst",
                                Pedigree = "ped_lst")) %>%
  mutate(Number_NA_Geno = as.factor(Number_NA_Geno)) %>%
  mutate(Number_NA_Geno = fct_inorder(Number_NA_Geno)) %>%
  ggplot(aes(x = Number_NA_Geno, y = Value)) +
  geom_boxplot() +
  facet_wrap(Data_Type ~ Group) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) +
  xlab("Number of Genotypes Without mRNA-Data") +
  ylab("Correlation Between Original and Imputed mRNA BLUEs")
```

>>>>

# Genotype-Wise mRNA-Imputation
```{r setup-impute, echo = FALSE}
pacman::p_load("sspredr", "tidyverse", "caret", "e1071", "viridis",
               "forcats", "knitr", "rmarkdown", "purrr", "rprojroot",
               "methods", "parallel")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ".", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 14, fig.height = 10, 
                      warning = FALSE, message = FALSE, echo = FALSE)
```

@@

```{r Plot-Correlation-Imputed-vs-NonImputed, cache = TRUE, fig.width = 12, fig.height = 12, fig.cap = "Pearson correlation coefficients between original and imputed mRNA genotypes for two heterotic groups and two sources of information (i.e. genomic and pedigree), depending on the number of genotypes without mRNA records. Genotypes without mRNA records were declared as such at random."}
par_lst <- readRDS("./data/derived/impute_single_mrna.RDS")
par_lst %>%
  map(~keep(., is_list)) %>%
  at_depth(.depth = 2, ~bind_rows(., .id = "Group")) %>%
  map(~bind_rows(., .id = "Replication")) %>%
  bind_rows(.id = "Data_Type") %>%
  mutate(Data_Type = fct_recode(Data_Type,
                                Genomic = "snp_lst",
                                Pedigree = "ped_lst")) %>%
  mutate(Number_NA_Geno = as.factor(Number_NA_Geno)) %>%
  mutate(Number_NA_Geno = fct_inorder(Number_NA_Geno)) %>%
  ggplot(aes(x = Number_NA_Geno, y = Value)) +
  geom_boxplot() +
  facet_wrap(Data_Type ~ Group, scales = "free") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 60, hjust = 1, vjust = 1)) +
  xlab("Number of Genotypes Without mRNA-Data") +
  ylab("Correlation Between Original and Imputed mRNA BLUEs")
```

### 2016-11-22 reports/index.Rmd
remove code boxes from report
Add legends to prediction legends

Chapter \@ref(prediction-for-reduced-data) deals with the results of hybrid 
prediction for the reduced set of data.

Chapter \@ref(prediction-with-imputed-mrnas) examines the influence of certain levels of missingness 
in the transcriptomic data.

>>>>

Chapter \@ref(transcriptomic-data) explores the distribution and correlations
of/among transcriptomic predictors for "raw" and transformed mRNA BLUEs.

Chapter \@ref(genotype-wise-mrna-imputation) examines the correlation between
the original and imputed transcriptomic BLUEs.

Chapter \@ref(loocv-prediction) deals with the results of hybrid prediction for 
the reduced set of data and a comparison of predictive abilities with the full 
data set.

### 2016-11-22 reports/loocv_reduced.Rmd
Add legends to prediction legends

# LOOCV-Prediction
```{r message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("tidyverse", "data.table", "dtplyr", "ggthemes", "viridis",
               "stringr", "forcats")

@@

Distribution of predicted and observed values.
Bear in mind that the distribution of the observed values will be different
for different predictors because some predictors "xx42" and "xx77", where
'xx' denotes a predictor, contain less hybrids than there are available 
(i.e. "xx100").
```{r Distribution-y-yhat, cache = TRUE}
legend_labs <- expression(y, hat(y))
distr_plot <- pred_df %>%
  filter(Predictor != "snp77-none-none") %>%
  gather(key = Value, value = `Phenotypic Value`, y, yhat) %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = `Phenotypic Value`, color = Value)) +
  geom_freqpoly() +
  scale_color_manual(values = viridis(length(legend_labs), option = "C"),
                     labels = legend_labs) +
  facet_grid(Predictor ~ Trait, scales = "free") +
  theme(legend.position = "top",
        strip.text.y = element_text(size = 5)) +
  ylab("Frequency")
```

Compare the coefficients of variation for all predictor-trait combinations.
```{r Coefficient-of-Variation-Plot, cache = TRUE}
cv_plot <- overview_df %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = CV, y = Predictor)) +
  geom_segment(aes(yend = Predictor), xend = 0, color = "gray50") +
  geom_point(aes(color = Predictor)) +
  scale_color_viridis(discrete = TRUE) +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.7, 0.13)
  ) +
  guides(color = guide_legend(ncol = 2,
                              reverse = FALSE)) +
  xlab("Coefficient of Variation") +
  ylab("Predictor Set") +
  xlim(0, NA)
```

Plot the predictive abilities for all predictor-trait combinations 
separately for the reduced and the full data set, respectively.
```{r Predictive-Ability-Plots, cache = TRUE}
pred_plot <- overview_df %>%
  as_tibble() %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order),
         Group = fct_relevel(Group, "Reduced", "Full")
  ) %>%
  ggplot(aes(x = Predictor, y = r)) +
  geom_bar(stat = "identity", aes(fill = Predictor), color = "black") +
  geom_text(aes(label = round(r, digits = 3)), vjust = -0.2) +
  scale_fill_viridis(discrete = TRUE, option = "inferno") +
  facet_grid(Trait ~ Group, space = "free", scales = "free_x") +
  theme_bw() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "bottom",
    legend.key = element_rect(color = "white")
  ) +
  guides(fill = guide_legend(nrow = 3,
                             byrow = TRUE,
                             keywidth = 0.25,
                             keyheight = 0.25,
                             default.unit = "inch",
                             title.position = "top")
  ) +
  ylim(c(0, 1))
```

>>>>

# LOOCV-Prediction
```{r setup-loocv, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("tidyverse", "data.table", "dtplyr", "ggthemes", "viridis",
               "stringr", "forcats")

@@

Distribution of predicted and observed values.
Bear in mind that the distribution of the observed values will be different
for different predictors because some predictors "xx42" and "xx77", where
'xx' denotes a predictor, contain less hybrids than there are available 
(i.e. "xx100").
```{r Distribution-y-yhat, cache = TRUE, fig.height = 12, fig.cap = "Frequency polygon of observed and predicted values for seven agronomic traits (columns) and nine sets of predictors (rows)."}
legend_labs <- expression(y, hat(y))
pred_df %>%
  filter(Predictor != "snp77-none-none") %>%
  gather(key = Value, value = `Phenotypic Value`, y, yhat) %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = `Phenotypic Value`, color = Value)) +
  geom_freqpoly() +
  scale_color_manual(values = c("#1f78b4", "#e31a1c"), labels = legend_labs) +
  facet_grid(Predictor ~ Trait, scales = "free") +
  theme_bw() +
  theme(legend.position = "top",
        strip.text.y = element_text(size = 7)) +
  guides(color = guide_legend(override.aes = list(size = 2))) +
  ylab("Frequency")
```

Compare the coefficients of variation for all predictor-trait combinations.
```{r Coefficient-of-Variation-Plot, cache = TRUE, fig.cap = "Coefficient of variation for seven agronomic traits and nine sets of predictors."}
overview_df %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order)) %>%
  ggplot(aes(x = CV, y = Predictor)) +
  geom_segment(aes(yend = Predictor), xend = 0, color = "gray50") +
  geom_point(aes(color = Predictor), size = 3) +
  scale_color_viridis(discrete = TRUE, option = "inferno") +
  facet_wrap(~ Trait, scales = "free_x") +
  theme_bw() +
  theme(panel.grid.major.y = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = c(0.7, 0.13)
  ) +
  guides(color = guide_legend(ncol = 2,
                              reverse = FALSE)) +
  xlab("Coefficient of Variation") +
  ylab("Predictor Set") +
  xlim(0, NA)
```

Plot the predictive abilities for all predictor-trait combinations 
separately for the reduced and the full data set, respectively.
```{r Predictive-Ability-Plots, cache = TRUE, fig.height = 10, fig.cap = "Predictive ability for seven agronomic traits (rows) and nine predictor sets (columns). The predictor sets are split into the categories 'Reduced' (i.e. 685 hybrids) and 'Full' (i.e. 1,521 hybrids)."}
overview_df %>%
  as_tibble() %>%
  filter(Predictor != "snp77-none-none") %>%
  mutate(Predictor = fct_relevel(Predictor, pred_order),
         Group = fct_relevel(Group, "Reduced", "Full")
  ) %>%
  ggplot(aes(x = Predictor, y = r)) +
  geom_bar(stat = "identity", aes(fill = Predictor), color = "black") +
  geom_text(aes(label = round(r, digits = 3)), vjust = -0.2) +
  scale_fill_viridis(discrete = TRUE, option = "inferno") +
  facet_grid(Trait ~ Group, space = "free", scales = "free_x") +
  theme_bw() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.title.x = element_blank(),
    legend.position = "bottom",
    legend.key = element_rect(color = "white")
  ) +
  guides(fill = guide_legend(nrow = 3,
                             byrow = TRUE,
                             keywidth = 0.25,
                             keyheight = 0.25,
                             default.unit = "inch",
                             title.position = "top")
  ) +
  ylim(c(0, 1))
```

### 2016-11-22 reports/na_fraction_pheno_predability.Rmd
Add legends to prediction legends

# Prediction with Imputed mRNAs
```{r message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE, message = FALSE)
```

>>>>

# Prediction with Imputed mRNAs
```{r setup-fraction, message = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6,
                      warning = FALSE, echo = FALSE, message = FALSE)
```

### 2016-11-22 reports/transcriptomic_data.Rmd
Add legends to prediction legends

# Transcriptomic Data
Keep only genotypes for which both, transcriptomic and genomic data are 
available.
```{r echo = FALSE}
pacman::p_load("sspredr", "tidyverse", "caret", "e1071", "viridis")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ".", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, 
                      warning = FALSE, message = FALSE, echo = FALSE)
```

>>>>

# Transcriptomic Data
Keep only genotypes for which both, transcriptomic and genomic data are 
available.
```{r setup-transcriptomic, echo = FALSE}
pacman::p_load("sspredr", "tidyverse", "caret", "e1071", "viridis")
knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ".", digits = 2)
})
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(fig.width = 8, fig.height = 6, 
                      warning = FALSE, message = FALSE, echo = FALSE)
```
